Modelling at-bats in baseball using the generalised Pareto distribution

### 2023-06-02 bibat/examples/baseball/docs/report.qmd

The final step was to document my analysis. To do this I edited the file
`docs/report.qmd`, then ran `quarto render docs/report.qmd`, which produced the
very HTML document that you are probably reading now! You can find the complete
`report.qmd` file
[here](https://github.com/teddygroves/bibat/blob/main/bibat/examples/baseball/docs/report.qmd).

>>>>

The final step was to document my analysis. To do this I edited the file
`docs/report.qmd`, then ran `make docs`, which produced the
very HTML document that you are probably reading now! You can find the complete
`report.qmd` file
[here](https://github.com/teddygroves/bibat/blob/main/bibat/examples/baseball/docs/report.qmd).
